---
title: "Applience exploration"
author: "Joan Claverol Romero"
date: "22/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# libraries
if (require(pacman) == FALSE) {
  install.packages("pacman")
}
pacman::p_load(tidyverse, lubridate, forecast, magrittr)
# load data
data <- read_rds("../../data/clean_data/processed_data.rds")
```

## Appliance exporation

GOAL: create an script to detect specific appliences

### Find out appliences

Where is the fridge?

```{r}
data %>% 
  select(date_time, Laundry) %>% 
  # filter(date(date_time) == "2007-02-06", between(hour(date_time), 3, 10)) %>% 
  filter(between(date(date_time),as_date("2010-01-01"),as_date("2010-01-05"))) %>% 
  ggplot(aes(x = date_time, y = Laundry)) +
    geom_line(color = "dodgerblue4") +
    theme_light() -> temp_p
plotly::ggplotly(temp_p)

```

There it is. How can we automaticly create a model to predict when is it going to turn on? We can cerate a time series object and then look if there is autocorrelation in the variable:

```{r}
# create time sereis witha sample form 1st quarter 2007
sample_data <- data %>% 
  filter(between(date(date_time),as_date("2007-01-01"),as_date("2007-01-03")))
ts_data <- ts(data = sample_data$Laundry, start = c(2007,1), frequency = 60*24)

autoplot(decompose(ts_data)) + theme_light()
```

Let's see if we can create a function to automaticly detect when the fridge is on:

```{r}
# create the sample data
sample_data <- data %>%
  filter(between(date(date_time),as_date("2007-01-01"),as_date("2010-11-26")))

output <- vector("double", length = nrow(sample_data))
  
# i <- 22
for (i in seq_along(sample_data$Laundry)) {
  # detect when the fridge turns on
  if (sample_data$Laundry[i-1] == 0 && 
      (sample_data$Laundry[i] == 1 || sample_data$Laundry[i] == 2) && 
      (sample_data$Laundry[i+1] == 1 || sample_data$Laundry[i+1] == 2)) {
    output[i-1] <- i-1
    output[i] <- i
  } 
  # detect the energy of the fridge once is turned on
  else if ((sample_data$Laundry[i-1] == 1 || sample_data$Laundry[i-1] == 2) && 
           (sample_data$Laundry[i] == 1 || sample_data$Laundry[i] == 2) &&
           (sample_data$Laundry[i+1] == 1 || sample_data$Laundry[i+1] == 2)) {
    output[i] <- i
  } 
  # detect the fridge before it turns off
  else if ((sample_data$Laundry[i-1] == 1 || sample_data$Laundry[i-1] == 2) &&
           (sample_data$Laundry[i] == 1 || sample_data$Laundry[i] == 2) && 
            sample_data$Laundry[i+1] == 0){
    output[i] <- i
    output[i+1] <- i+1
  }
}
```


```{r}
# create a tibble with fridge information
fridge <- tibble(id = output)

fridge %<>% 
  mutate(id = as.character(id)) %>% 
  filter(id != 0) %>% 
  left_join(y = sample_data %>% 
              rownames_to_column(var = "id") %>% 
              select(id, date_time, Laundry), by = "id") %>% 
  drop_na() %>% 
  write_rds("../../data/clean_data/fridge_data.rds")
```


```{r}
temp <- fridge %>% 
  head(100)

temp %>% 
  mutate(engine = if_else(Laundry == 0, "Off", "On"))


fridge_on_off <- fridge %>% 
  filter(Laundry == 0)

temp <- fridge_on_off
output <- vector(length = nrow(fridge_on_off), mode = "double")

for (i in seq(0, length(temp$Laundry), 2)) {
  output[i-1] <- paste0("fridge_",i) 
  output[i] <- paste0("fridge_",i)
}

fridge_on_off$name <- output

fridge_semi_label <- fridge %>% 
  left_join(fridge_on_off %>% select(id, name), by = "id")

label <- fridge_semi_label$name

for (i in seq_along(label)) {
  row <- 1
  while (is.na(label[i])) {
    label[i] <- label[i-row]
    row <- row+1
  }
}

energy_time <- vector(mode = "double", length = length(label)-1)

time <- 0
for (i in seq_along(energy_time)) {
  if (label[i] == label[i+1]) {
    energy_time[i] <- time 
    time <- time + 1
  } else {
    time <- 1
  }
}

fridge_semi_label$name <- label
fridge_semi_label$energy_time <- c(energy_time, 0)

fridge_energy <- fridge_semi_label %>% 
  group_by(name) %>% 
  summarise(n = sum(Laundry)) %>% 
  rowid_to_column(var = "time")


library(gganimate)
theme_set(theme_bw())

fridge_semi_label %>% 
  filter(year(date_time) == 2007, name == "fridge_2") %>%
  ggplot(aes(x = energy_time, y = Laundry)) +
    geom_line() +
    transition_time(name) +
    labs(title = "Fridge: {frame_time}")
```

