---
title: 'Exploration and data analysis'
author: "Joan Claverol Romero"
date: "21/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, fig.align = "center")
# library 
if (require(pacman) == FALSE) {
  install.packages("pacman")
}
pacman::p_load(fpp2, tidyverse, lubridate, plotly, beanplot, tibbletime)
# load data ----
df <- read_rds("../../data/raw_data/household_power_consumption.rds")
```

## Exploration and data analyisis

### Data quality problems:

* 

### Time analysis

We can detect there are different gaps in the data variable with missing values:



### Missing values

```{r}
# load data with daylight savings
df <- read_rds("../../data/clean_data/day_light_savings.rds")
# find missing values
df %>% 
  group_by(year = year(date_time), 
           month = month(date_time, label = T, abbr = T)) %>% 
  summarise_all(~sum(is.na(.))) %>% 
  ggplot(aes(x = month, y = Global_active_power)) +
    geom_col(fill = "dodgerblue4") +
    facet_wrap(~year) +
    labs(title = "Quantity of missing values by month") +
    theme_minimal() +
    theme(
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, size = 10), 
      axis.title.x = element_blank()
    )
```

#### season effect

```{r}
# load data
df <- read_rds("../../data/clean_data/processed_data.rds")

df %>% 
  group_by(date = date(date_time)) %>% 
  summarise(mean = mean(ActiveEnergy)) %>%
  ggplot(aes(date, mean)) + 
    geom_line(color = "dodgerblue4", alpha = 0.4) + 
    geom_smooth(color = "dodgerblue4", se = F) + 
    labs(title = "Mean active energy consumed by day") + 
    ylab("Watt/h") + xlab("Time") + 
    theme_light()
```

Yes, there is a seasonality on the data, so the season has an influence in the energy consumption: In winter there is a high consumption and in summer there is less consumption. Important to consider that the season in our model. 

Another way to show the same information:

```{r}
df %>% 
  mutate(month = month(date_time, label = T), 
         year = year(date_time)) %>% 
  group_by(year, month) %>% 
  summarise(mean_A.E. = mean(ActiveEnergy)) -> x

ts <- ts(x$mean_A.E., start = 2007, frequency = 12)
ggsubseriesplot(ts) + theme_bw()
```

#### week day effect

```{r}
df %>% 
  mutate(wday = wday(date_time, label = T, abbr = F, week_start = 1), 
         hour.minutes = paste(hour(date_time), 
                              minute(date_time), 
                              second(date_time), sep = ":")) %>% 
  group_by(wday, hour.minutes) %>% 
  summarise(median = round(median(ActiveEnergy),2)) -> week.general

week.general$hour.minutes <- as.POSIXct(strptime(week.general$hour.minutes, 
                                                 format = "%H:%M:%S", tz = "GMT"), 
                                        format = "%H:%M:%S")

week.general %>% 
  ggplot(aes(hour.minutes, median)) + 
    geom_line(col = "dodgerblue4") + 
    facet_wrap(wday~.) + 
    scale_x_datetime(date_labels = "%H:%M") +
    labs(title = "Median active energy/week") + 
    ylab("Median Watt/h") + xlab("Time") + 
    theme_light() + 
    theme(
      axis.title.x = element_blank()
    )
```

Yes, there is diffent energy consumption in relation to the day of the week:

* Monday to Friday they follow similar patterns
* Saturday the most different day of the whol week
* Sunday ALso different to the resto of the week, but has similitudes
* And we can also see that there are different consumptions in the morning, miday and evening.

##### Understanding the distribution of each wday for the whole year {.tabset}

###### Boxplots

```{r}
week.general %>% 
  ggplot(aes(wday, median)) + 
  geom_boxplot(col = "dodgerblue4") +
  labs(title = "Kw/h distribution by week day") +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank()
  )
  # No outliers
```

###### Beanplots

```{r}
beanplot(week.general$median ~ week.general$wday, col = c("blue", "red", "yellow"))
```

#### submetter analyisis

```{r}
# Are the submeters collecting all the possible information
x <- c("Kitchen","Laundry","W.A_HeatCold","UnkownEnergy")

df %>% 
  select(season, x) %>% 
  gather(x, key = submeters, value = energy_consumption) %>% 
  group_by(season, submeters) %>% 
  summarise(energy_consumption = sum(energy_consumption)) -> submPerc

# define colors to use 
cbp1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

brks <- c(0, 0.25, 0.5, 0.75, 1)
submPerc %>%
  ggplot(aes(season, energy_consumption)) + 
    geom_col(aes(fill = submeters), position = "fill") +
    scale_fill_manual(values = cbp1) +
    labs(title = "Energy consumption by season") +
    scale_y_continuous(breaks = brks, labels = scales::percent(brks)) +
    ylab("% submters") + xlab("Season") + 
    theme_minimal() +
    theme(
     axis.title.x = element_blank() 
    )
```

